\documentclass[letterpaper,11pt]{article}
\usepackage[pagesetup]{tucv}
\usepackage[colorlinks=true,urlcolor=black]{hyperref}
\fancyfoot[C]{Philip Tricca - \thepage}

\begin{document}

% renew resjob command to get rid of weird line break in date range
\RenewDocumentCommand\resjob{ommm}{
    \resentry[10pt]{
    \setlength{\parskip}{1ex plus 0.5ex minus 0.2ex} \textbf{#2}
    \IfNoValueTF{#1}
    {}
    {\newline #1}
    }{\mbox {#3 - #4}}
}

% Page heading and name/contact info table
\begin{tabular*}{7in}{l@{\extracolsep{\fill}}r}
\textbf{\Large Philip B. Tricca}
& flihp@twobit.us \\
San Bruno CA, 94066
& http://twobit.us \\
\end{tabular*}

\resheading {Qualification Summary}
Computer Engineer with 7 years experience in a government research environment
and 6 years analyzing, designing, and building security oriented Linux-based
products and tools. Strong technical, organizational and planning skills.
Professional, trustworthy and a natural communicator. Dedicated to technical
excellence in software design, implementation and documentation with a focus
on security.

\resheading {Key Qualifications}
\begin {itemize}
  \setlength {\itemsep}{1pt}
  \setlength {\parskip}{0pt}
  \setlength {\parsep}{0pt}
  \item Transformed Intel's TPM2 Software Stack (TSS2) from one-person
    prototype to healthy Open Source Software (OSS) project by embracing
    community best practices and processes, rigorous unit and integration
    testing, heavy use of continuous integration \& automation tools and
    role modeling inclusive behavior.
  \item Delivered software releases on predictable schedule balancing
    requirements from corporate customers and upstream Linux Distributions
    (RedHat, Suse etc) through release management and feature planning
    activities.
  \item Successfully transitioned hardware root of trust prototype from
    research project developed in government research lab to Citrix product.
\end {itemize}

\resheading {Professional Experience}
\resemployer {Intel}{\mbox{Santa Clara, CA}}
\resjob [
  Performs design and development tasks to promote the adoption and correct
  use of platform security technologies. Primary tasks include:
]{Platform Architect, Platform Security Division}{10/2014}{present}
\begin {itemize}
  \setlength {\itemsep}{1pt}
  \setlength {\parskip}{0pt}
  \setlength {\parsep}{0pt}
  \item Design and implementation of TSS2 APIs and plumbing. All API
    design done collaboratively with the Trusted Computing Group (TCG)
    TSS2 working group. Source code implementing the TSS2 libraries,
    system daemon and tools based on TCG specifications published and
    maintained as OSS: \url{https://github.com/tpm2-software/}
  \item Identification of high value usage models for
    Intel\textsuperscript{\textregistered} SGX. Duties include analysis
    and documentation of threat models as well as impact to system
    security. Designs and documentation are peer reviewed, socialized
    with customers before moving on to prototype development.
\end {itemize}

\resemployer {Citrix Systems}{\mbox{Bedford, MA}}
\resjob [
  Oversaw the open source release of the XenClient XT client
  virtualization product as the OpenXT project.
  Additional responsibilities included:
]{Architect, Client Virtualization Group}{10/2013}{07/2014}
\begin {itemize}
    \setlength {\itemsep}{1pt}
    \setlength {\parskip}{0pt}
    \setlength {\parsep}{0pt}
  \item Design and implementation of virtual disk encryption component.
  \item Lead customer requirement collection and design review.
\end {itemize}
\resjob [
  Developer on XenClient XT product: a client hypervisor focused on strong
  separation and security properties. Primary customers include government
  defense agencies. Contributions to this project include:
]{Senior Software Engineer, Client Virtualization Group}{08/2011}{10/2013}
\begin {itemize}
  \setlength {\itemsep}{1pt}
  \setlength {\parskip}{0pt}
  \setlength {\parsep}{0pt}
  \item Design and implementation of platform measured launch using the
    TPM, Intel\textsuperscript{\textregistered} TXT and the OpenEmbedded
    build framework.
  \item Defining and documenting threat models and the software
    architectures that defend against them.
  \item Development of platform mandatory access control policy (SELinux /
    XSM).
  \item Collecting requirements from customers and evaluators / testers
    for the purpose of knowledge transfer and certification.
\end {itemize}

\resemployer {Air Force Research Lab}{\mbox{Rome, NY}}
\resjob [
  Performed a mix of work on research efforts relevant to military needs
  in the area of information systems security and contract management.
]{Computer Engineer, Information Directorate}{07/2004}{08/2011}
\begin {itemize}
  \setlength {\itemsep}{1pt}
  \setlength {\parskip}{0pt}
  \setlength {\parsep}{0pt}
  \item Lead Engineer on SecureView project. Responsible for security
    architecture, technical design and customer reviews.
  \item Design improvements to ``Guard'' systems through the application
    of mandatory access control mechanisms and information flow principles.
  \item Maintain relationships with security community through academic
    and industry conferences.
  \item Contract management and technical guidance of cooperative research
    agreements with academic institutions including Cornell and PSU
    totaling over \$2M.
\end {itemize}

\resemployer {Open Source Software}{}
\resjob [
  Contributing code, testing and/or debugging to open source projects.
  Active community participant asking \& answering questions on public
  mailing list and issue trackers.
] {Contributor} {01/2010} {present}
\begin {itemize}
  \setlength {\itemsep}{1pt}
  \setlength {\parskip}{0pt}
  \setlength {\parsep}{0pt}
  \item Creator and maintainer of the meta-measured OpenEmbedded layer to
    automate measured launch in embedded-style build environment.
    Currently listed in the official OE layer index.
  \item Contributor to the meta-selinux and meta-virtualization
    OpenEmbedded layers.
  \item Dual purpose work on Masters Project and XenClient XT:
    Integration of SELinux with XenClient management stack to separate
    mutually distrusted QEMU processes (sVirt architecture).
\end {itemize}

\resheading{Education}
\begin{itemize}
  \item[]
  \resschool{Syracuse University}{New York}
  \resdegree[
    Software Security and Systems Assurance\\
    Advisor: Dr. Wenliang (Kevin) Du
  ]{M.S.}{Computer Engineering}{2006-2012}
  \resdegree[
    Focus of study: Software Engineering with a specific focus on system
    programming in i386 Assembly and C.
    Graduated Magna Cum Laude
  ]{B.S.}{Computer Engineering}{2000-2004}
\end{itemize}

\resheading{Awards}
\begin {itemize}
  \setlength {\itemsep}{1pt}
  \setlength {\parskip}{0pt}
  \setlength {\parsep}{0pt}
  \item Key Contributor Award.
    Trusted Computing Group.
    2017-11-01
  \item Outstanding Engineering Professionalism Award.
    Mohawk Valley Engineers Executive Council.
    2010-02-18
  \item Special recognition of service from the Commander for service
    rendered while leading Commander Directed Investigation, 2009.
\end {itemize}

\resheading {Public Speaking \& Publications}
\begin {itemize}
\item {\it TPM2 Software Stack: Device Driver to Event-Driven Applications}
  Linux Plumbers Conference
  Los Angeles, California.
  2017
  URL: \url {http://www.linuxplumbersconf.org/2017/ocw/sessions/4675.html}
\item {\it Securing Embedded Linux Systems with TPM2}.
  Embedded Linux Conference
  Portland, Oregon.
  2017.
  URL: \url {https://www.youtube.com/watch?v=0qu9R7Tlw9o}
\item {\it In-Guest Mechanisms to Strengthen Guest Separation}.
  Xen Summit co-located with LinuxCon.
  Edinburgh, Scotland,
  2013.
  URL: \url {https://www.youtube.com/watch?v=6Q8mlTBn-ZI}
\item {\it A pipeline development toolkit in support of secure information flow goals}.
  Proceedings of the 5th Annual CSIIR Workshop : Cyber Security and Information Intelligence Challenges and Strategies.
  Oak Ridge, Tennessee.
  2009.
\end{itemize}

\resheading {Representative writing samples}
\begin {itemize}
  \setlength {\itemsep}{1pt}
  \setlength {\parskip}{0pt}
  \setlength {\parsep}{0pt}
\item TCG TSS2 async APIs and event driven programming:
  \url {https://blog.twobit.us/2017/10/15/tcg-tss2-async-api-event-driven/}
\item TrEE vs TCG: Dueling TPM2 Specs:
  \url {http://blog.twobit.us/2015/11/tree-vs-tcg/}
\item Attaching a TPM on the LPC:
  \url {http://blog.twobit.us/2015/02/attaching-tpm-on-lpc/}
\item Measured launch on OE-Core:
  \url {http://blog.twobit.us/2013/01/meta-measured/}
\item An on-going series documenting my masters project implementing the sVirt architecture on XenClient:
  \url {http://blog.twobit.us/tag/mastersproject/}
\item A two part series describing the ``why'' and ``how'' of configuring a network driver domain on Xen:
  \url {http://blog.twobit.us/2010/07/xen-network-driver-domain-wh/}
  \url {http://blog.twobit.us/2010/07/xen-network-driver-domain-how/}
\end {itemize}

\resheading {Relevant Technical Proficiencies}
\begin {itemize}
  \setlength {\itemsep}{1pt}
  \setlength {\parskip}{0pt}
  \setlength {\parsep}{0pt}
  \item TPM2 \& TCG TSS2 API and infrastructure concepts and implementation
    on Linux and Windows.
  \item GNU Autotools build and parallel test harness.
  \item Test strategies and test driven development methodologies.
  \item Continuous integration and test automation: travis-ci, coveralls,
    cmocka etc.
  \item Open Source Software development and project management /
    maintainership with 5 years experience maintaining large C code
    base.
  \item Proficiency with the OpenEmbedded build system and the construction of meta layers / distros.
  \item Flask policy development and system configuration (SELinux / XSM).
  \item Appropriate usage of the TPM for constructing measured software systems.
  \item Threat modeling software systems using the STRIDE methodology.
  \item Appropriate usage of OpenSSL APIs (EVP/RAND).
  \item Programming in popular languages (shell,C,Python), quickly learns new languages as needed.
  \item Professional / technical writing and documentation suitable for submission as project deliverables.
  \item Proficiency with popular OSS tools and work flows.
  \item Document preparation in \LaTeX.
\end {itemize}

\end {document}
